---
title: "RBasic"
author: "Marco Chiapello"
date: "06 July 2016"
output: 
  beamer_presentation:
    theme: "Rochester"
    colortheme: "dove"
---

## Outlook

\textbf{Wednesday afternoon}

- Introduction

- Data types
  
- Data manipulation

- Read Data

- Plotting

\textbf{Thursday morning}

- Exercise

- Work on your data

- Write functions

#============================
## Introduction

R is a free software.

R is a statistical software.

R is powerfull. (This presentation has been made in R)

R has a wide community of supporters

R is popular.

#============================
## Introduction







#============================
## R and RStudio installation

**R** => http://www.r-project.org

**RStudio** => http://www.rstudio.com


## Data types
1. Vector
```{r}
x <- c(1,2,3,4,5,6,7,8,9)
x
```








2. Matrix
```{r}
y <- matrix(x, nrow = 3)
y
```









## Data manipulation

```{r}
1 + 1
4 - 5
2 * 2
4 / 2
```

## Data manipulation

Built-in functions
```{r}
sqrt(25)
abs(-2)
log2(2)
```

